---
title: "Prediction Analysis of Stopping Distance"
output:
  ioslides_presentation: default
  slidy_presentation: default
date: "July 1, 2017"
---


## Introduction

This presentation is the second part of the Course Project for the Developing Data Products class. This peer assessed assignment has two parts. First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

The Shiny application was created based on the Cars dataset in R, which give the speed of cars and the distances taken to stop. Note that the data were recorded in the 1920s.

The app for the first part is available at:
https://chen2365.shinyapps.io/develop_data_product/
<br>
Source code are available at:
https://github.com/chen2365/develop-data-product


## Cars Dataset
Examples of the data point in the dataset:
```{r, echo=FALSE}
head(cars)
```
The summary of the Cars dataset is the following:
```{r, echo=FALSE}
summary(cars)
```

## Predict the Stopping Distance
We simply run a linear regression on the stopping distance against the driving speed of the car, using the historical data recorded in the 1920s. Then we predict the stopping distance based on the linear model.
The embedded is the following:
```{r, eval=FALSE}
predictionModel<-lm(dist~speed, data = cars)

  modelPred <- reactive({
    speedinput<- input$sliderSpeed
    predict(predictionModel, newdata = data.frame(speed = speedinput))
  })
```

## URLs

The app delopyed on the R Shiny server is available at:
<br>
https://chen2365.shinyapps.io/develop_data_product/
<br>
Source code for ui.R and sever.R files are available at the GitHub:
https://github.com/chen2365/develop-data-product


